Analysis - expt 1

### 2024-12-11 code/expt_1/analysis_1.Rmd
start cogsci

correctness <- dat %>% select(game, trial=trialNum, target, distractor, correct)
transcript %>% filter(!is.na(description)) %>% group_by(game,speaker, trial) %>% 
  summarize(words=str_c(description, sep=" ", collapse=", ")) %>% 
  left_join(correctness) %>% 
  mutate(word_count=str_count(words, "\\S+")) %>% 
  mutate(type=case_when(trial<2 ~ "practice",
                        trial<6 ~ "block 1",
                        trial<10 ~ "block 2",
                        trial<14 ~ "block 3")) %>% 
  ggplot(aes(x = trial+1, y = word_count, color=type)) +
    geom_jitter(width=.2, height=0, alpha=.5)+
  #geom_line(aes(group=game))+
 # facet_wrap(.~correct) + 
    stat_summary(fun.data="mean_cl_boot", geom="pointrange", color="black") +
  scale_color_manual(values=time_palette)+
  #geom_bar(position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  #geom_smooth(method="lm")+
  #geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("\nTrial") +
  #coord_cartesian(ylim=c(0,60))+
  #ylab("Percent trials with echoing \n by experimenter\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  #scale_y_continuous(breaks=seq(0,100,10), expand=c(0,0)) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")

>>>>

correctness <- dat %>% select(game, trial=trialNum, target, distractor, correct)

transcript %>% filter(!is.na(description)) %>% group_by(game,speaker, trial) %>% 
  summarize(words=str_c(description, sep=" ", collapse=", ")) %>% 
  left_join(correctness) %>% 
  mutate(word_count=str_count(words, "\\S+")) %>% 
  mutate(type=case_when(trial<2 ~ "practice",
                        trial<6 ~ "block 1",
                        trial<10 ~ "block 2",
                        trial<14 ~ "block 3")) %>% 
  ggplot(aes(x = trial+1, y = word_count, color=type)) +
    geom_jitter(width=.2, height=0, alpha=.5)+
  #geom_line(aes(group=game))+
 # facet_wrap(.~correct) + 
    stat_summary(fun.data="mean_cl_boot", geom="pointrange", color="black") +
  scale_color_manual(values=time_palette)+
  #geom_bar(position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  #geom_smooth(method="lm")+
  #geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  theme_classic() +
  xlab("\nTrial") +
  #coord_cartesian(ylim=c(0,60))+
  #ylab("Percent trials with echoing \n by experimenter\n") +
  #scale_x_continuous(breaks=seq(1,12,1)) +
  #scale_y_continuous(breaks=seq(0,100,10), expand=c(0,0)) +
  theme(aspect.ratio = 4/5,
        axis.title=element_text(size=14,face="bold"),
        axis.text=element_text(size=9, color = "black"),
        legend.position = "none")
